### 2021-04-23 input/related_work.tex
positioning

Content indexing in geo-distributed infrastructures has been studied
through various approaches.  Offering an indexing service which is
either hosted by a centralized entity or distributed through nodes of
the network has long been the predominant one. This mainly requires
(i) to have access to the list of current replica locations and (ii)
to be aware of the topology to compute which replica is the closest
for a given location.

(i) Deploying a centralized server that maintains an index of all
replica locations has been proposed in~\cite{snamp, p2p-oracle,
  fogstore, p2p-alto}. These solutions suffer from well-known
disadvantages inherent to centralized solutions (load balancing,
robustness, locality, etc.) that are even magnified in an Edge
context.  Distributing this index among nodes in the network
circumvent some of these issues, either using coordinate-based
overlays~\cite{voronet, coin_19} or \underline{D}istributed
\underline{H}ash \underline{T}ables (DHT)~\cite{ipfs, mdht, squirrel}
for example. In the latter, each node stores a part of the index,
defined by an interval between hash values.  Before downloading any
object, a node first hashes the content to obtain the address of the
node that stores the replica locations of this given object. After
obtaining from the remote node the list of available replicas, it can
select the closest copy to download from. We emphasize that, in this
setting, the DHT only stores information about replicas locations, not
the content itself. DHT-based approaches are well-studied and easy to
deploy in order to offer such a localization service.

(ii) Being centralized or distributed, this index should be enhanced
with the topology knowledge in order to be able to decide where
resides the closest replica. Maintaining a consistent view of an ever
changing topology across a network is inherently complicated,
especially in asynchronous settings. This is a well-studied problem in
the network community and numerous protocols have been proposed. As
for the index, this knowledge about the topology can be either
centralized~\cite{topology-discovery} or distributed like in routing
protocols such as \underline{O}pen \underline{S}hortest
\underline{P}ath \underline{F}irst (OSPF).

@@

At first glance, membership protocols as proposed in~\cite{t-man}
would appear to provide suitable abstractions to create a
scope-related partitioning, as proposed in this paper. Such protocols
usually rely on gossip mechanism, implying contacts with random nodes
that can be very far away in the physical topology. Moreover,
membership protocols are usually implemented by modifying the
neighboring of a given node according to a certain metric in a logical
overlay.  On the contrary, we do not aim at building any overlay, as
we only rely on the physical topology so the neighbors of a given node
are not continuously modified. Lastly, these protocols are usually
cycle-based, meaning that they impose a constant load on the network
traffic, even when the system state does not change. Likewise, this
also prevents from using solutions that periodically advertise their
cache content~\cite{garcia-lopez, hemmati2015namebased} as they also
incur an overhead even in quiet contexts without any update.
Moreover, such solutions necessarily rely on physical timeouts that
could lead to either premature removals of partitions when they are
still operating; or slow convergence where processes wrongly believe
they belong to a partition that was removed.

>>>>

Content indexing in geo-distributed infrastructures has been studied
through various approaches.  Offering an indexing service which is
either hosted by a centralized entity or distributed through nodes of
the network has long been the predominant one. This mainly requires
\begin{inparaenum}[(i)]
\item to have access to the list of current replica locations and
\item to be aware of the topology to compute which replica is the
  closest for a given location.
\end{inparaenum}

Deploying a centralized server that maintains an index of all replica
locations has been proposed in~\cite{snamp, p2p-oracle, fogstore,
  p2p-alto}. These solutions suffer from well-known disadvantages
inherent to centralized solutions (load balancing, robustness,
locality, etc.) that are even magnified in an Edge context.
Distributing this index among nodes in the network circumvent some of
these issues, either using coordinate-based overlays~\cite{voronet,
  coin_19} or \underline{D}istributed \underline{H}ash
\underline{T}ables (DHT)~\cite{ipfs, mdht, squirrel} for example. In
the latter, each node stores a part of the index, defined by an
interval between hash values.  Before downloading any object, a node
first hashes the content to obtain the address of the node that stores
the replica locations of this given object. After obtaining from the
remote node the list of available replicas, it can select the closest
copy to download from. We emphasize that, in this setting, the DHT
only stores information about replicas locations, not the content
itself. DHT-based approaches are well-studied and easy to deploy in
order to offer such a localization service.

Being centralized or distributed, this index should be enhanced with
the topology knowledge in order to be able to decide where resides the
closest replica. Maintaining a consistent view of an ever changing
topology across a network is inherently complicated, especially in
asynchronous settings. This is a well-studied problem in the network
community and numerous protocols have been proposed. As for the index,
this knowledge about the topology can be either
centralized~\cite{topology-discovery} or distributed like in routing
protocols such as \underline{O}pen \underline{S}hortest
\underline{P}ath \underline{F}irst (OSPF).

@@

At first glance, membership protocols as proposed in~\cite{t-man}
would appear to provide suitable abstractions to create a
scope-related partitioning, as proposed in this paper. Such protocols
usually rely on gossip mechanism, implying contacts with random nodes
that can be very far away in the physical topology. Moreover,
membership protocols are usually implemented by modifying the
neighboring of a given node according to a certain metric in a logical
overlay.  On the contrary, we do not aim at building any overlay, as
we only rely on the physical topology so the neighbors of a given node
are not continuously modified. Lastly, these protocols are usually
cycle-based, meaning that they impose a constant load on the network
traffic, even when the system state does not change. Likewise, this
also prevents from using solutions that periodically advertise their
cache content~\cite{garcia-lopez, hemmati2015namebased} as they also
incur an overhead even in quiet contexts without any update.
Moreover, such solutions necessarily rely on physical timeouts that
could lead to either premature removals of partitions when they are
still operating; or slow convergence where processes wrongly believe
they belong to a partition that was removed. On the opposite
Section~\ref{sec:experimentation} shows that \NAME quickly converges
to consistent partitioning even in large scale networks.
